Medical Concept Extraction

### 2012-12-17 paper/paper.tex
Final pass through Code Architecture.

\section{System}
This section discusses the framework code we have developed in order to perform concept extraction, the web service frontend which allows users to test the service without seeing any of the underlying data, and the machine learning libraries that are leveraged.

@@

Our framework consists of many convenience functions and utilities classes that are designed to perform all necessary file I/O operations formatting output data and parsing input files. There are 3 formats that the code base handles.

@@

The third and last format is is a sparse matrix format that is utilized by the various command-line utilizes in the code base. Conceptually, the rows in this sparse matrix represent an a single data item (in our case, a single word) that either is a training example or is an input token that needs to a label predicted and the columns represent the various features of that item. The various learning algorithms all use this data format.

@@

Our framework includes a model class that can be trained on certain data with certain features enabled. The model class supports training a libsvm, liblinear, and crfsuite classifiers that can be used for prediction in the future. One of the nice things, about the model class is that it can be serialized and reloaded dynamically. This is a really nice capability because it allows you to train a large number of models on various subsets of the data and using various different features to see which perform the best.

@@

As mentioned previously, the framework's model class has support for training various classifiers: a Support Vector Machine, a CRF, and L2-regularized Support Vector Machine. The implementation of these algorithms is delegates to various third-party libraries described below.

@@

\item {\tt data/<data-set-name>/txt } - Contains the raws tokenized text files.

@@

\item {\tt models/<model-name>/predictions/} - Contains output files with the predicted label for each word in the input file.

>>>>

\section{System}
The system we have developed consists of a framework in order to perform concept extraction, a web service frontend which allows users to test the service without seeing any of the underlying data, and the machine learning libraries that are leveraged.

@@

Our framework consists of many convenience functions and utility classes that are designed to perform all necessary file I/O operations--formatting output data and parsing input files. There are 3 formats that the code base handles.

@@

The third and last format is is a sparse matrix format that is utilized by the various command-line utilizes in the code base. Conceptually, the rows in this sparse matrix represent an a single data item (in our case, a single word) that either is a training example or is an input token that needs to a label predicted and the columns represent the various features of that item. Each of the various learning algorithms use this data format.

@@

Our framework includes a model class that can be trained on specified data with any combination of features enabled. The model class supports training a libsvm, liblinear, and crfsuite classifiers that can be used for prediction in the future. One of the nice things, about the model class is that it can be serialized and reloaded dynamically. This is a really nice capability because it allows you to train a large number of models on various subsets of the data and using various different features to see which perform the best.

@@

As mentioned previously, the framework's model class has support for training various classifiers: a Support Vector Machine, a CRF, and L2-regularized Support Vector Machine. The implementation of these algorithms is delegated to various third-party libraries described at the end of this section.

@@

\item {\tt data/<data-set-name>/txt } - Contains the raw tokenized text files.

@@

\item {\tt models/<model-name>/test_predictions/} - Contains output files with the predicted label for each word in the input file.
